\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Software Engineering student with hands-on experience delivering full-stack and performance-focused software solutions using Python, TypeScript, React Native, Firebase, C++, and Rust. Built and shipped user-facing applications, optimized backend algorithms, and collaborated in team environments while proactively identifying missing information, testing thoroughly, and iterating on small to medium complexity features. Actively seeking an 8-month software engineering co-op starting May 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Languages}{: Python, TypeScript, JavaScript, C++, Rust, SQL}  \\              \textbf{Frontend \& Mobile}{: React, React Native}  \\              \textbf{Backend \& Data}{: Node.js, Firebase}  \\              \textbf{Tools \& Development}{: Git, Linux (Arch)}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Google Gemini API, Python, TypeScript }}{}
      
            \resumeItemListStart
                  \resumeItem{ Engineered a cross-platform mobile application from scratch as measured by a production product with paying users, by delivering user-facing features in React Native and Firebase for aquarium management. }
                  \resumeItem{ Built a verified species data pipeline as measured by a cleaned database of 650+ freshwater fish species, by developing Python scrapers to gather facts, validate records, and organize structured application data. }
                  \resumeItem{ Integrated AI-assisted identification and guidance as measured by eliminating manual lookups from routine user workflows, by connecting Google Gemini APIs for image recognition and aquarium care support. }
                  \resumeItem{ Implemented product engagement features as measured by recurring subscription revenue and automated reminder workflows, by adding monetization, email funneling, and Google Calendar-based notifications. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ URepair Web Platform } $|$ \emph{ C++, React, Node.js }}{}
      
            \resumeItemListStart
                  \resumeItem{ Optimized backend search performance as measured by a 60\%+ improvement in query response time, by implementing and refining matching algorithms and data structures in C++. }
                  \resumeItem{ Delivered web platform functionality as measured by a completed contractor-to-job matching system, by building frontend and backend features with React, Node.js, and C++. }
                  \resumeItem{ Applied structured problem solving as measured by 3 sorting algorithms and 3 data structures evaluated for job matching, by identifying performance issues and generating straightforward technical solutions. }
                  \resumeItem{ Collaborated effectively in an agile team as measured by shared delivery across a 3-person project, by using Git to exchange ideas, review progress, and contribute features with minimal supervision. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Quantum Time Wave Universe Simulation } $|$ \emph{ Rust }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a simulation engine as measured by a working 2D model with real-time rendering, by implementing numerical wave propagation logic in Rust across a grid of Planck-node states. }
                  \resumeItem{ Improved simulation capability as measured by successive upgrades from 2-vector to 3-vector state representations, by iterating on system design and adapting the mathematical model as new issues were identified. }
                  \resumeItem{ Delivered advanced interactive behavior as measured by stable skyrmions and observable multi-particle interactions, by adding vacuum decay, Skyrme-force logic, momentum, and pushing functions to the simulation. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Validated robotics equations as measured by 100+ test cases, by modeling human-gait kinematics in Python and MATLAB and using test-driven development to confirm expected behavior. }
                  \resumeItem{ Contributed to team execution as measured by weekly research progress alignment, by sharing findings through GitLab updates and proactively seeking clarification from a professor and peer researcher. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Supported infrastructure delivery as measured by installing 20 km of control wiring per week, by contributing to capacitor bank and control-building upgrade work at BC Hydro Kennedy Substation. }
                  \resumeItem{ Executed complex field tasks as measured by successful site upgrade and demobilization progress, by assisting with bus bar upgrades, platform extensions, guard rail work, and firestopping across electrical penetrations. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}