\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Software Engineering student and Electrical Apprentice who builds practical, data-driven software systems that reduce guesswork and turn ambiguous problems into reliable products. Built AI-enabled applications, verified a 650+ record species dataset, improved backend query speed by over 60\%, and validated research code with 100+ test cases. Actively seeking an 8-month software engineering co-op starting May 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Languages}{: C++, Rust, Python, TypeScript, MATLAB}  \\              \textbf{Frameworks \& Platforms}{: React, React Native, Node.js, Firebase, Google Gemini API}  \\              \textbf{Developer Tools \& Practices}{: Git, Linux, Test-Driven Development, Web Scraping}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Google Gemini API, Python, TypeScript }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a cross-platform mobile app from scratch using React Native and Firebase, including user authentication, subscriptions, and Google Calendar reminder flows. }
                  \resumeItem{ Built a Python pipeline that scraped, cleaned, and verified a database of over 650 freshwater fish species, improving data quality for downstream recommendations. }
                  \resumeItem{ Integrated Google Gemini API features for image recognition and aquarium care guidance, then marketed the product with zero budget and acquired paying users. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ URepair Web Platform } $|$ \emph{ C++, React, Node.js }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a web platform in a 3-person agile team connecting contractors to job opportunities, using Git for version control and React and Node.js for the interface. }
                  \resumeItem{ Implemented and tested 3 sorting algorithms and 3 data structures in a C++ backend to strengthen job-matching performance and reliability. }
                  \resumeItem{ Optimized search logic to improve query response times by over 60\%, reducing friction for users trying to find relevant opportunities quickly. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Ray Tracing Engine } $|$ \emph{ Rust, C++ }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built a 3D ray tracer from scratch in Rust and C++ without using graphics APIs, implementing rays, materials, primitives, and matrix transforms. }
                  \resumeItem{ Optimized rendering performance by 300\% with a bounding volume hierarchy and parallelized the workload with multithreading to accelerate compute-heavy experimentation. }
                  \resumeItem{ Incorporated physics-based gravitational lensing around a black hole, translating an ambiguous simulation problem into a working visual system. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Modeled and verified kinematic equations for mimicking human gait using Python and MATLAB, translating ambiguous research goals into testable mathematical functions. }
                  \resumeItem{ Validated 100+ test cases with test-driven development and shared progress through weekly meetings and GitLab updates with a professor and student collaborator. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Installed roughly 20km of control wiring per week during BC Hydro Kennedy Substation capacitor bank upgrades, contributing to control building and bus bar upgrades in a safety-critical environment. }
                  \resumeItem{ Completed firestopping across the dam and powerhouse at electrical penetrations and participated in demobilization at Site C, maintaining disciplined execution on complex infrastructure work. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}