\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Software engineering student and electrical apprentice who builds reliable data-driven products and performance-focused systems in fast-moving, ambiguous environments. Has built AI-enabled products, cleaned and verified datasets of 650+ records, and optimized software systems by 60\% through deliberate testing and iteration. Actively seeking an 8-month software engineering co-op starting May 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Languages}{: Python, SQL, C++, JavaScript, MATLAB}  \\              \textbf{Data \& Backend}{: ETL/ELT, Data Modeling, Firebase, Node.js, Relational Databases}  \\              \textbf{Tools \& Collaboration}{: Git, React Native, Test-Driven Development}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Python, TypeScript, Google Gemini API }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a cross-platform React Native app from scratch and built a Python scraper that pulled, cleaned, and verified a database of 650+ freshwater fish species for use in the product. }
                  \resumeItem{ Integrated Google Gemini image recognition and a fine-tuned chatbot to identify fish, plants, or diseases and deliver aquarium care guidance. }
                  \resumeItem{ Implemented Firebase authentication and database workflows, subscription features, and Google Calendar reminder integration, then marketed the app with zero budget and acquired paying users. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ URepair Web Platform } $|$ \emph{ C++, React, Node.js, Git }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed the backend in C++ and the frontend in React and Node.js for a web platform connecting contractors to job opportunities. }
                  \resumeItem{ Implemented and tested three sorting algorithms and three data structures to improve job matching logic. }
                  \resumeItem{ Optimized search algorithms and reduced query response times by over 60\% while collaborating in a 3-person agile team using Git. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Custom RF Antenna Tracker } $|$ \emph{ Python, RTL-SDR, Raspberry Pi Zero, J-Pole Antenna }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built and tuned a J-pole antenna and developed a handheld tracking device using a Raspberry Pi Zero and RTL-SDR for targeted radio frequency monitoring. }
                  \resumeItem{ Wrote Python scripts to perform TDOA multilateration and locate a signal transmitter within an 11-meter accuracy radius. }
                  \resumeItem{ Implemented logic that compared local transmission times with repeater transmission times to increase TDOA precision. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Modeled and validated kinematic equations for mimicking human gait in Python and MATLAB, using test-driven development and 100+ test cases. }
                  \resumeItem{ Shared progress through GitLab and weekly meetings with a professor and another student to clarify goals and stay aligned on the research direction. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Installed roughly 20 km of control wiring per week during capacitor bank upgrades at BC Hydro Kennedy Substation, contributing to a large-scale substation modernization effort. }
                  \resumeItem{ Completed firestopping at electrical penetrations across the dam and powerhouse and assisted with site demobilization to prepare the project for handoff to BC Hydro. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}