\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Adaptive field-ready problem solver and Software Engineering student who turns ambiguous technical work into reliable data, practical tools, and clear communication for end users. Built and validated species data pipelines, monitoring tools, and research models, including a Python workflow that cleaned and verified 650+ species records and a robotics project tested with 100+ cases. Actively seeking a 4-month summer position starting May 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Software \& Data}{: Python, C++, React Native, Firebase}  \\              \textbf{AI \& Research}{: Google Gemini API, MATLAB, Data Validation, Testing}  \\              \textbf{Field Technology}{: ESP32, PCB Design, RTL-SDR, High Voltage Safety}  \\              \textbf{Communication \& Workflow}{: Git, Technical Reporting, User Education}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Google Gemini API, Python, TypeScript }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built a cross-platform mobile app for aquarium management using React Native and Firebase, giving users a practical tool for species identification and care decisions. }
                  \resumeItem{ Developed a Python web scraper that pulled, cleaned, and verified data for over 650 freshwater fish species, improving the quality of information behind the app's guidance. }
                  \resumeItem{ Integrated Google Gemini image recognition and a specialized chatbot, then marketed the product with zero budget to acquire paying users. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Custom RF Antenna Tracker } $|$ \emph{ RTL-SDR, J-Pole, Python }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built and tuned a physical J-pole antenna for targeted radio-frequency monitoring in a real-world field setup. }
                  \resumeItem{ Wrote Python scripts for TDOA multilateration that located a signal transmitter within an 11-meter accuracy radius, reducing uncertainty during physical search work. }
                  \resumeItem{ Improved tracking precision by comparing local transmission times with repeater transmission times, iterating toward more reliable field measurements. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Smart Fertilizer Doser } $|$ \emph{ ESP32, C++, 3D Printing, PCB Design, Python }}{}
      
            \resumeItemListStart
                  \resumeItem{ Designed and fabricated a custom PCB for a smart aquarium fertilizer doser with peristaltic pump drivers and capacitive fluid level sensors. }
                  \resumeItem{ Developed ESP32 firmware in C++ with a state machine that managed four dosing channels, safety checks, and error handling for more reliable operation. }
                  \resumeItem{ Built an internal dosage calculator based on tank volume and solution concentration, translating messy biological inputs into consistent treatment decisions. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Modeled and verified kinematic equations for mimicking human gait using Python and MATLAB, validating mathematical functions with 100+ test cases to improve confidence in the results. }
                  \resumeItem{ Shared progress through GitLab and weekly meetings with a professor and another student, keeping ambiguous research work transparent and aligned. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Installed roughly 20 km of control wiring per week during BC Hydro Kennedy Substation capacitor bank upgrades, contributing dependable field execution on a large industrial site. }
                  \resumeItem{ Upgraded bus bar, guard rails, platforms, and firestopping around electrical penetrations while maintaining careful high-voltage safety standards. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}