\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Data-focused software engineering student and electrical apprentice with foundations in Python, SQL, and operational problem solving, building reliable systems that turn messy inputs into usable tools. Proven through a Python workflow that pulled, cleaned, and verified 650+ species records for an AI-enabled app, backend optimization that improved query response times by over 60\%, and research validation using 100+ test cases. Actively seeking an 8-month software engineering co-op starting May 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Languages}{: Python, SQL, C++, TypeScript, JavaScript, MATLAB}  \\              \textbf{Data \& AI}{: Data Cleaning, Data Validation, ETL/ELT Concepts, Google Gemini API}  \\              \textbf{Frameworks \& Platforms}{: React Native, Node.js, Firebase, Git}  \\              \textbf{Systems \& Analysis}{: RTL-SDR, Algorithm Optimization}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Google Gemini API, Python, TypeScript }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built a cross-platform aquarium management app from scratch using React Native and Firebase, then integrated Google Gemini AI for image recognition and aquarium care guidance. }
                  \resumeItem{ Developed a Python scraper that pulled, cleaned, and verified a database of more than 650 freshwater fish species, improving data quality for in-app recommendations and search. }
                  \resumeItem{ Designed a signup-to-email pipeline and launched a zero-budget marketing funnel that acquired paying subscribers, validating product-market fit and iterating the product around real user behavior. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ URepair Web Platform } $|$ \emph{ C++, React, Node.js, Git }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a web platform connecting contractors to job opportunities in a 3-person agile team, using Git to coordinate backend and frontend work. }
                  \resumeItem{ Implemented and tested 3 sorting algorithms and 3 data structures in C++ to improve job matching logic and reduce uncertainty in search results. }
                  \resumeItem{ Optimized search algorithms to improve query response times by over 60\%, accelerating how quickly users could find relevant jobs. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Custom RF Antenna Tracker } $|$ \emph{ Python, RTL-SDR, Raspberry Pi Zero, J-Pole }}{}
      
            \resumeItemListStart
                  \resumeItem{ Built and tuned a J-pole antenna for targeted radio-frequency monitoring, creating the signal capture layer for a handheld tracking system. }
                  \resumeItem{ Wrote Python scripts to perform TDOA multilateration and locate a transmitter within an 11-meter accuracy radius. }
                  \resumeItem{ Improved evidence quality by comparing local transmission times with repeater transmission times, substantially increasing TDOA precision under real-world conditions. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Modeled and verified kinematic equations for mimicking human gait using Python and MATLAB, translating ambiguous research goals into testable functions. }
                  \resumeItem{ Validated mathematical functions with more than 100 test cases using test-driven development and kept work transparent through weekly progress meetings with another student and the professor. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Installed roughly 20 km of control wiring per week during BC Hydro Kennedy Substation capacitor bank upgrades, contributing to a large, safety-critical operational environment. }
                  \resumeItem{ Completed firestopping at electrical penetrations and upgraded guard rails, capacitor bank platforms, bus bar, and wiring routes to support reliable site handoff to BC Hydro. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}