\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{\small #1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Bradley D. Schmidt} \\ \vspace{5pt}
    \small Kamloops, BC $|$ \href{mailto:Bradleyschmidt04@gmail.com}{\underline{Bradleyschmidt04@gmail.com}} $|$ 
    \href{tel:7785868196}{\underline{778-586-8196}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
{\small Software engineering student and electrical apprentice focused on building practical web and engineering tools that connect AI, data workflows, and real-world systems for faster, better-informed work. Proven through an AI-enabled mobile product with a verified 650+ species data pipeline, a React and C++ web platform that improved query response times by over 60\%, and robotics research that validated kinematic models with 100+ test cases. Actively seeking an 8-month software engineering co-op starting September 2026. }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
             \textbf{Languages}{: Python, C++, TypeScript, JavaScript, MATLAB, SQL}  \\              \textbf{Web \& Application Development}{: React, React Native, Node.js, Firebase}  \\              \textbf{AI, Data \& Collaboration}{: Google Gemini API, Git, GitLab, Test-Driven Development}  \\              \textbf{Engineering Tools}{: CAD, 3D Printing}          }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
          \resumeProjectHeading
          {\textbf{ AquaFlora Mobile App } $|$ \emph{ React Native, Firebase, Google Gemini API, Python, TypeScript }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a cross-platform aquarium management app from scratch using React Native, Firebase, Python, and TypeScript, and implemented monthly subscriptions for monetization. }
                  \resumeItem{ Built a Python data pipeline that scraped, cleaned, and verified a database of over 650 freshwater fish species, improving information quality for in-app care decisions. }
                  \resumeItem{ Integrated Google Gemini AI for image recognition and chatbot guidance so users could identify fish, plants, or diseases from tank photos and receive targeted care recommendations. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ URepair Web Platform } $|$ \emph{ C++, React, Node.js, Git }}{}
      
            \resumeItemListStart
                  \resumeItem{ Developed a web platform connecting contractors to job opportunities using React, Node.js, and C++. }
                  \resumeItem{ Implemented and tested 3 sorting algorithms and 3 data structures for job matching, comparing approaches before deployment. }
                  \resumeItem{ Optimized search algorithms to improve query response times by over 60\% while collaborating in a 3-person agile team using Git. }
              \resumeItemListEnd
            
          \resumeProjectHeading
          {\textbf{ Steam Deck Dual Screen Prototype } $|$ \emph{ CAD, 3D Printing, Hardware Prototyping }}{}
      
            \resumeItemListStart
                  \resumeItem{ Designed a custom dual-screen and phone-mount attachment for the Steam Deck in CAD and iterated 3D-printed prototypes to achieve a precise snap-fit. }
                  \resumeItem{ Sourced components and evolved the concept from a simple phone mount into a proprietary screen attachment that connected directly to the system. }
                  \resumeItem{ Validated demand by launching an Etsy shop, selling about 20 units at \$60 each, and managing manufacturing, quality control, and shipping end to end. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
        { Robotics Research Assistant }{ May 2024 -- Jun. 2024 }
        { Thompson Rivers University }{}
      
            \resumeItemListStart
                  \resumeItem{ Modeled and verified kinematic equations for mimicking human gait using Python and MATLAB, translating mechanics concepts into testable software models. }
                  \resumeItem{ Validated mathematical functions with 100+ test cases using test-driven development and communicated progress through GitLab and weekly meetings with a professor and another student. }
              \resumeItemListEnd
            
          \resumeSubheading
        { Electrical Apprentice }{ Jun. 2025 -- Present }
        { F\&M Installations Ltd. }{}
      
            \resumeItemListStart
                  \resumeItem{ Installed about 20 km of control wiring per week during BC Hydro Kennedy Substation capacitor bank upgrades, contributing to control building, platform, and bus bar upgrade work in a high-safety environment. }
                  \resumeItem{ Completed firestopping at electrical penetrations across the dam and powerhouse using rockwool firestop bricks and red caulk while supporting site demobilization for BC Hydro handoff. }
              \resumeItemListEnd
            
      \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thompson Rivers University}{Kamloops, BC}
      {Bachelor of Engineering in Software Engineering, 4th Year}{Expected Apr. 2027}
  \resumeSubHeadingListEnd

\end{document}